---
title: "Mozfest 2014 CDE"
author: "JLM"
date: "26 October 2014"
output: html_document
---

```
require('reshape2')
```

First, grepped out the indicator code:

    head -n 1 GPOutcomes/results.csv > p01133.csv
    grep "P01133" GPOutcomes/results.csv >> p01133.csv
    
Got 24735 data lines.
    
```{r}
p01133 <- read.csv('p01133.csv')
```

Discovery: The data we need is already there. Just look at P01133C.

```{r}
prevalence <- subset(p01133, Indicator_Code == 'P01133C')
hist(prevalence$Value)
```

Calculate national prevalance. Estimated number is 'P01133A'; registered number of cases is 'P01133B'.

```{r}
sum(subset(p01133, Indicator_Code == 'P01133B')$Value) /
  sum(subset(p01133, Indicator_Code == 'P01133A')$Value)
```

Get this into a nicer form, with one column per value we want.

```{r}
pKeys <- c('Practice_Code', 'Practice_Name', 'Indicator_Code', 'CCG', 'SHA_Code', 'SHA_Name', 'PCT_Code', 'PCT_Name')
pMelt <- melt(p01133[,c(pKeys, 'Value')], pKeys)
pCast <- dcast(pMelt, Practice_Code + Practice_Name + CCG + SHA_Code + SHA_Name + PCT_Code + PCT_Name ~ Indicator_Code + variable)
```

Aggregate up by CCG.

```{r}
pCCG <- aggregate(cbind(registered=P01133B_Value, estimated=P01133A_Value) ~ CCG, data = pCast, sum)
pCCG <- transform(pCCG, prevalence = 1000*registered / estimated)
names(pCCG)[1] <- 'ccg_code'
write.csv(file="data/pCCG.csv", pCCG, row.names=FALSE)
```

Make some breaks for the nice spruce leaf plot:

```{r}
print(paste(seq(from=0,to=8,length.out=8), collapse=", "))
```